---
title: "PrePost"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PrePost}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = TRUE, 
  comment = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  results = "hide"
)
```

## Connecting to the database
First, generate the artificial data (sqlite files for each database), as follows:
```{r setup}
library(PrePost)

# generate example databases
prepost_example()
```

This will create a folder called gendata in your working directory, containing the database files
for the example cohort. Next, you can connect to this databases using:

```{r connect}
library(PrePost)
library(dplyr)
library(icdb)

# connect to ICB server using this
# srv <- icdb::server("[data_source_name]"])  #see ICDB documentation for details

# in this example we can connect to the synthetic data using
srv <- example_server()
```
## Define the cohort
Here an example cohort is provided on the example server. All we need is the
(pseudo) NHS number and the datetime of interest.
```{r cohort}
ids  <- srv$cohort$COHORT_SYNTH %>% select(nhs_number) %>% pull()
date <- srv$cohort$COHORT_SYNTH %>% select(index_event_time) %>% pull() %>% as.POSIXct()

```

## Define the activity filters
Here we must decide which healthcare activity we are interested in. We can define any number of filters to act on SWD activity columns, as a named list. The name of each filter will be used in the subsequent plots.
```{r activity_coverage}
activity_filter <- list(
  "A+E"                 = "pod_l1=='secondary' & pod_l2a=='ae'",
  "Community in-person" = "pod_l1=='community' & pod_l3=='physical'",
  "999"                 = "pod_l1=='999'",
  "111"                 = "pod_l1=='111'",
  "GP"                  = "pod_l1=='primary_care_contact'"
)
```

## Create the PrePost object
Next we create a PrePost object, defining the window of interest. If working on the ICB servers you
will need to pass the name of your ICB data source as the parameter `srv_name`. Please see the ICDB package documentation for instructions on how to setup the ICB data source. In this example we directly pass an example_server - this is purely for demonstration.
```{r prepost_obj}
obj <- PrePost(nhs_number       = ids,
               index_event_time = date,
               window_pre       = 31,
               window_post      = 30, 
               window_units     = "days",
               activity_filter  = activity_filter,
               svr              = example_server(), 
               svr_name         = NA_character_)
```

## Descriptives
Run the descriptive analysis
```{r descriptives, results='markup', fig.dim = c(7, 5)}
run_descriptives(obj)
```

## Activity analysis
Run the activity analysis
```{r activity_tables, results='markup', fig.dim = c(7, 5)}
run_activity_summary(obj, "before")
run_activity_summary(obj, "after")
```

## Theographs 
Generate the theographs
```{r generate_theographs, results='markup', fig.dim = c(7, 5)}
generate_theographs(obj)
```

## Activity volume
Analyse the activity volume
```{r activity_volume}
run_activity_volume(obj, "before")
run_activity_volume(obj, "after")
```

## Trace plots 
Generate the trace plots
```{r trace_plots, results='markup', fig.dim = c(7, 5)}
generate_trace_plots(obj, "before")
generate_trace_plots(obj, "before")
generate_trace_plots(obj, "around")
```
