---
title: "PrePost"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PrePost}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = TRUE, 
  comment = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  results = "hide"
)
```

# Connecting to the database

First, generate the artificial data (sqlite files for each database), as follows:
```{r setup}
library(PrePost)

# generate example databases
prepost_example()
```

This will create a folder called gendata in your working directory, containing the database files
for the example cohort. Next, you can connect to this databases using:

```{r connect}
library(PrePost)
library(dplyr)
library(icdb)

# connect to ICB server using this
# srv <- icdb::server("[data_source_name]"])  #see ICDB documentation for details

# in this example we can connect to the synthetic data using
srv <- example_server()
```

Define the cohort - here an example cohort is provided on the example server. All we need is the
(pseudo) NHS number and the datetime of interest.
```{r cohort}
ids  <- srv$cohort$COHORT_SYNTH %>% select(nhs_number) %>% pull()
date <- srv$cohort$COHORT_SYNTH %>% select(index_event_time) %>% pull() %>% as.POSIXct()

```

Next we create a PrePost object, defining the window of interest. If working on the ICB servers you
will need to pass the name of the data source as the parameter `srv_name`.
```{r prepost_obj, include=FALSE}
obj <- PrePost(nhs_number       = ids,
               index_event_time = date,
               window_pre       = 31,
               window_post      = 30, 
               window_units     = "days",
               svr              = example_server())
```

Run the descriptive analysis
```{r descriptives, results='markup', fig.dim = c(7, 5)}
run_descriptives(obj)
```
